Paper Title (Something about Applying LIME to Bullet Data)

### 2018-09-19 paper/Paper Title.Rmd
paragraph on test set 224

---
title: "Paper Title (Something about Applying LIME to Bullet Data)"
author: "Katherine Goode and Heike Hoffman"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
---

@@

# Explain the Data (TS 224)

@@

>>>>

---
title: "Paper Title (Something about Applying LIME to Bullet Data)"
author: "Katherine Goode and Heike Hofmann"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
bibliography: references.bib
---

@@

# The Hamby 224 Clone

The Hamby 224 Clone is organized as a test set of a cloned (sub-)set of the Hamby 224 bullets. As with all Hamby sets [@hamby], Hamby set 224, is a collection of 35 bullets, organized as 20 known bullets and 15 questioned bullets. The known bullets are fired in pairs of two through one of ten consecutively manufactures P-85 barrels.
Clone set 224 is arranged as a test set of fifteen tests, one for each questioned bullet. Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet. The test asks for a decision on whether the questioned bullet comes from the same source as the two known bullets  or from a different source. This situation is similar to what a Firearms and Toolmarks Examiner might encounter in case work.

@@

# References
